### 2015-04-13 signature.tex
move up quotes on dedication page, format changes on signature page

\underline{\hspace{4.2in}}\\
\youradvisor\\
Dissertation Advisor \hspace{2.3in}Date

@@

\underline{\hspace{4.2in}}\\
\departmenthead\\
Head, Department of Mathematics and Statistics \hspace{0.27in}Date

@@

\underline{\hspace{4.2in}}\\
Dean, Graduate School \hspace{2.12in}Date

>>>>

\underline{\hspace{4.2in}}\\
\youradvisor\\
Dissertation Advisor \hspace{2.43in}Date

@@

\underline{\hspace{4.2in}}\\
\departmenthead\\
Head, Department of Mathematics and Statistics \hspace{0.6in}Date

@@

\underline{\hspace{4.2in}}\\
Dean, Graduate School \hspace{2.27in}Date
